Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2020-12-30 GWLDCII.tex
final read through

Meanwhile, a different body of work has studied SYM $N=4$ theory from the point of view of Feynman integrals in twistor space \cite{Adamo:2011pv,Adamo:2012xe,  Boels:2007qn, Bullimore:2010pj}. These integrals are calculated via holomorphic Wilson loops. As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams, and adding up the corresponding sums of Feynman integrands associates a volume form to a convex space different from those in the decomposition the Amplituhedron \cite{CachazoSvrcekWitten, Hodges2013}.

Wilson loop diagrams, as we will study them, are objects given by a perturbative expansion of the holomorphic Wilson loop in twistor space.
Classically, the interactions of the theory were studied as maximal helicity violating diagrams ($MHV$ diagrams), next-to-maximal helicity violating diagrams and so on ($N^kMHV$ diagrams) in momentum space. Adamo and Mason, in \cite{Adamo:2011pr}, gave an elegant formulation for the $N^kMHV$ diagrams in twistor space. The Wilson loop diagram perspective of this paper is dual to this twistor representation of $N^kMHV$ diagrams.
The objects are closely related and carry the same information.  We choose to emphasize the dual perspective by our focus on the Wilson loop diagrams.

@@

As described above, each integrand associated to a Wilson loop diagram gives the volume of a convex polytope. However, each individual tree level integral has singularities. These singularities are of two types: physical and spurious.  The physical singularities come from special kinematical points and we will not consider them in this paper.  The spurious singularities come from zeros of the denominator of the integral, and hence are accessible to our combinatorial techniques.  SYM $N=4$ is a finite theory so we only expect to see the physical singularites in the overall amplitude.  Consequently, the spurious singularities are artifacts of how the integrals are represented and must cancel in the calculation of a tree level scattering amplitude, though the details of how the cancellations come about remain unclear. The cancellation has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$-dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto \cite{generalcombinatoricsI}.

@@

One may also interpret the functional $I(W)$ as associating a volume to each cell $\Sigma(W)$ \cite{wilsonloop, Amplituhedronsquared, HeslopStewart}, where the volume is determined by the external particles involved. Specifically, the integrand is written in terms of the elements of $C(W)$ as  \begin{equation} \label{eq:omega(W) def}\Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V(p_r)} \textrm{d}x_{p_r}}{R(W)} \;, \end{equation} multiplied by a $\delta$ function that evaluates the matrix $C(W)$ on the external particles. The denominator $R(W)$ is given in Definition~\ref{def R(W)} below.

@@

\begin{lem}\label{lem sian}
  Let $W$ be a weakly admissible Wilson loop diagram with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two conditions holds.
  \vspace{-0.5em}
  \begin{enumerate}
    \item $W$ has a propagator of length at most 6 with a propagator of length 2 on one side of it and nothing else on that side.\label{item big and 2}
    \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator has an end between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
  \end{enumerate}
See Figure~\ref{fig: small configs} for an illustration of the two configurations.
\end{lem}

@@

Since each propagator is removed by the algorithm after it contributes, each propagator contributed exactly once to $I_i$, making the above ordering well defined.
Note that different $I_*$ impose different orderings on the propagators. Furthermore, we will see below that this ordering respects the ordering of vertices in $I_i$, i.e. if $p_j$ occurs before $p_l$ in the ordering imposed by $I_i$, then we also have $I_i(p_j) <_i I_i(p_l)$. This will follow directly from Corollary \ref{GN alg well defined}.
\end{rmk}

@@

To construct $I_1$ we start at vertex 1, so we set $i=1$, $j = 1$, and $I_1 = \emptyset$. 
\begin{itemize}
\item $j = 1$: Since $\Prop(1) = \{q,r\}$ and $r$ is the clockwise-most of these propagators, $r$ contributes at this step. We let $I_1 = \{1\}$ and remove propagator $r$ from the diagram. 
\item $j = 2$: $\Prop(2) = \{p,q\}$, with $q$ being the clockwise-most of these propagators, so $q$ contributes at this step. We now have $I_1 = \{1,2\}$ and propagator $q$ is removed.
\item $j = 3$: $\Prop(3) = \{p\}$, so we have $I_1 = \{1,2,3\}$ and we remove propagator $p$. The only remaining propagator in the diagram is $s$.
\item $j = 4$: Since $p$ and $q$ were removed in earlier steps, we now have $\Prop(4) = \emptyset$.
\item $j = 5$: $\Prop(5) = \{s\}$, and we have $I_1 = \{1,2,3,5\}$.
\end{itemize}
There are no propagators left in the diagram, so the algorithm terminates and we have ${I_1 = \{1,2,3,5\}}$, which we write more compactly as $1235$. 
%So the propagators are ordered $r,q,p,s$ with respect to $I_1$, and 
$I_1$ viewed as a function is given by
\[I_1: \cP \longrightarrow [n] : \quad I_1(r) = 1,\quad I_1(q) = 2, \quad I_1(p) = 3, \quad I_1(s) = 5.\]
Applying the algorithm for all 8 starting vertices, we obtain the sets
\[1235, 2356, 3456, 4567, 5671, 6712, 7812, 8123.\]
The reader can easily verify that this sequence of $k$-sets satisfies the definition of a Grassmann necklace, and can (with significantly more work) also verify that this Grassmann necklace defines the positroid $M(W)$ associated to the Wilson loop diagram $W$ above. We will prove this in general shortly.
\end{eg}

@@

\begin{figure}
\[
\begin{tikzpicture}[baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLDfragment[8]{4}{0.3}
	%\drawnumbers % use this to debug
	%\clip (\zero + 1.5*\step:1.5*\radius) rectangle (345:{\radius});
	\centerarc[linehighlight](0,0)(\zero + 2.8*\step:\zero + 6.2*\step:\radius)
	\newnode[below]{1}{i}
	\newnode[below]{2}{i+1}
	\newnode[below]{3}{l}
	\newnode[below]{4}{l+1}
	\newnode[below]{5}{l+2}
	\newnode[below]{6}{l+3}
	\newnode[below]{7}{j}
	\newnode[below]{8}{\quad j+1}
	%\node[rotate=-15] at (\zero + 2.7*\step:\radius) {\Large $($};
	%\node[rotate=15] at (\zero + 6.3*\step:\radius) {\Large $)$};
	\node at (\zero + 4.5*\step:\radius*0.85) {\em \scriptsize up to 4 vertices here};
	\begin{scope}
	\clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
		\draw[smallpropagator] (\zero+1.3*\step:\radius*1.2) to [bend left = 40] (\zero + 7.7*\step:\radius*1.2); 
	\node at (\zero + 4.5*\step:\radius*0.5){\footnotesize $q$};
\end{scope}
\end{scope}
\end{tikzpicture}
\]
\caption{Diagram $V$ is $W$ with $p$ removed; there are no propagators inside $q = (i,j)$, though there may be up to 4 non-supporting vertices labelled $l, l+1, \ldots$.}
\label{fig V diagram}
\end{figure}

@@

We first calculate $I^{W}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$. Note that $p$ has no effect on other propagators for starting vertices in this range (since $p$ will be the final propagator encountered by the algorithm) so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$. Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ contributes a vertex in the diagram $V$, i.e. on the value of $I^{V}_w(q)$. Thus, if $w\in J_q^{V}(i)$ then 
    \[
    I_w^{W}(r) =  \begin{cases}
        \max\{i+1, m\} & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{V}(i+1)$ or $w\in J_q^{V}(j)$ then
    \[
    I_w^{W}(r) =  \begin{cases}
        l & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p \;.
      \end{cases} 
      \]
We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$. For the majority 
%$w \in [l, l+a-1]$} 
%I left this as a comment so we can add it in if necessary, but I don't think we need this level of precision in this sentence: we're just signposting what we're going to do in detail shortly.
of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{W}$, then the remainder of $I_w^{W}$ proceeds identically to the assignments of $I^{V}_{w+1}$ (recall Remark~\ref{rmk algorithm locally same}).  Thus we have for any $0\leq b <a$
    \[
    I_{l+b}^{W}(r) = \begin{cases}
      l+b & \text{if } r=p\\
      I_{l+b+1}^{V}(r) & \text{if } r\neq p\;.
    \end{cases}
    \]
Similarly, if $j$ is in the support of $p$, then we have
     \[
       I_j^{W}(r) = \begin{cases}
         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
         I_{j+1}^{V}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$} \;.
       \end{cases} 
       \]
If $j$ is not in the support of $p$, then we must be in Case 2 of Figure~\ref{fig 3 cases} with two vertices in the right hand region.  In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.

@@

For $w \in [n]\backslash\{j+1,m,m+1,m+2,m+3\}$, if $w\in J_q^{V}(i)$ or $w\in J_q^{V}(i+1)$ then
    \[
    I_w^{W}(r) =  \begin{cases}
        m & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} 
    \]
    while if $w\in J_q^{V}(j)$ then
    \[
    I_w^{W}(r) =  \begin{cases}
        \max\{m, j+1\} & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} \;.
    \]

@@

Let $W'$ be the diagram obtained from $W$ by removing the propagator $p$.  We have
\begin{align*}
  I_i^{W} \backslash \{i\} & = I_{i+1}^{W'} \\
  I_{i+1}^{W} \backslash \{i+1\} & = I_{i+2}^{W'}
\end{align*}
since in both cases the algorithm in $W'$ proceeds identically to that in $W$ after assigning $p$. Since $m \neq i+1$, we have $m\in I_{i+1}^{W'}\setminus\{i+1\}$ but $m\not\in I_{i+2}^{W'}$, contradicting the minimality of $W$. This completes the proof.
\end{proof}

@@

Note that the positroid cells associated to the Amplituhedron are of dimension $4|\cP|$. In \cite[section 2]{non-orientable}, Agarwala and Marcott associated a Deodhar component\footnote{Since Deodhar components play no role in this paper, the interested reader is referred to \cite{non-orientable} for more details on this.} to each Wilson loop diagram, and showed that the dimension of this Deodhar component is the sum of $|\cP|$ and the dimension of the associated positroid cell.
%\[|\cP| + \text{ the dimension of associated positroid cell}.\]
Combining this with Theorem~\ref{thm dim}, we see that the Deodhar component associated to a Wilson loop diagram is $4|\cP|$-dimensional, showing that the geometry underlying the Wilson loop diagrams is consistent with the geometry underlying the Amplituhedron. It is worth noting that the Amplituhedon is defined by a projection of a set of $4|\cP|$ dimensional positroid cells, while the $3|\cP|$-dimensional cells of the Wilson loop diagram lie in $\mathbb{G}_\R$.
While it is conjectured that the geometry of the Amplituhedron is related to the geometry of the Wilson loop diagrams, in part due to their common physical origin, the $3 |\cP|$ dimensional positroid cells defined by the Wilson loop diagrams do not seem to bear any geometric relationship to the $4|\cP|$ dimensional cells parametrized by the Amplituhedron.
%To  date, there is no evidence to suggest that the $3|\cP|$ dimensional positive cells of $\Gr(|\cP|, n)$ defining the Wilson loop diagrams are related to the $4|\cP|$ dimensional positive cells defining the Amplituhedron.  \sanote{This para adresses point 3 of report Y. Should there be a similar paragraph in the intro? Should it be moved?} \sanote{futzed some  more}

@@

\begin{lem}\label{lem I}
Let $W$ be an admissible Wilson loop diagram with $k\geq 1$ propagators, and suppose $W$ admits one of the configurations described in Lemma~\ref{lem good p}, with $p$ and $q$ (if $q$ exists) both of length 2. Let $V$ be $W$ with $p$ removed.  We can express $I_*^W$ in terms of $I_*^V$ as indicated below.

  \begin{align*}
    I_1^{W} & = I_1^{V} \cup \{n-3\} \\
    I_n^{W} & = I_1^{V} \cup \{n\} \\
    I_{n-1}^{W} & = I_n^{V} \cup \{n-1\} \\
    I_{n-2}^{W} & =
    \begin{cases}
      I_{n-2}^{V}\cup \{n-2\} & \text{if $n-2\not\in I_{n-2}^{V}$} \\
      I_{n-2}^{V}\cup \{n-1\} & \text{if $n-2\in I_{n-2}^{V}$, $n-1\not\in I_{n-2}^{V}$} \\
      (I_{n}^{V} \setminus \{n-5\})\cup \{n-1,n-2\} & \text{if $n-1, n-2\in I_{n-2}^{V}$}
    \end{cases} \\
    I_{k}^{W} & =
    \begin{cases}
      I_k^{V}\cup \{n-3\} & \qquad \qquad \qquad \qquad \text{if $n-3 \not\in I_k^{V}$}\\
      I_k^{V}\cup\{n-2\} & \qquad \qquad \qquad \qquad \text{if $n-3\in I_k^{V}$}
    \end{cases} \\
    & \text{for $1<k<n-2$}
  \end{align*}
\end{lem}

@@

Finally, if $n-2$ and$ n-1$ are in $I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but some other propagator must have contributed $n-1$ to $I_{n-2}^{V}$ so we cannot use the same argument as above.  When, in the algorithm, the construction of $I_{n-2}^W$ reaches vertex $n$, only the propagators $p$ and $q$ have contributed; thus we proceed as in the construction of $I_n^{V}$ but without propagator $q$ by Remark \ref{rmk algorithm locally same}. By Lemma~\ref{vertex cyclic int lem} we know that $I_n^V(q) = n-5$, and from Remark \ref{clockwise ordering rem} we see that the only way this could occur is if $q$ was the last to contribute to $I_{n-2}^V$. %all other propagators in $V$ had already been assigned when we reached vertex $n-5$; thus $q$ was the final propagator contributing to $I_n^{V}$. 
Therefore, $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$ in this case. This completes all cases for $I_{n-2}^{W}$.

@@

To avoid wordiness, we will refer to the row indexed by $i$ in the Le diagram as row $i$ or the $i$ row, and similarly for columns.  Note that the $i$ row in this sense is not the $i^{th}$ row since the indexing for Le diagrams does not label the rows sequentially starting at $1$, and so to avoid confusion we will not refer to the $i^{th}$ row.

@@

\begin{eg}
Consider the Wilson loop diagram in Figure~\ref{fig R eg}. Assigning propagators $p$, $q$, $r$ to rows $1,2,3$ respectively, we obtain the matrix
\[
C(W) = \begin{bmatrix} a & b & 0 & 0 & 0 & c & d \\ e & f & 0 & 0 & g & h & 0 \\ i & j & 0 & k & l & 0 & 0 \end{bmatrix}.
\]
The Grassmann necklace of this diagram is
\begin{gather*}(I_1 = \{1,2,4\},\ I_2 = \{2,4,5\},\ I_3 = \{4,5,6\},\ I_4=\{4,5,6\},\\ I_5=\{5,6,7\},\ I_6 = \{6,7,1\},\ I_7=\{7,1,2\}). \end{gather*}  
Figure~\ref{fig R eg} indicates which vertex is contributed to $I_i$ by each propagator, for each $i \in [1,7]$.

@@

Finally, we have $r_1 = (af-be)k$.  Putting the previous calculations together, we obtain
\[
R = (af-be)kgbclhdi(ej-fi)
\]
which is square-free and contains all factors of $\prod_{i=1}^{n}\Delta_{I_i}$. If one were to construct the denominator $R(W)$ associated to this Wilson loop diagram as per Definition~\ref{def R(W)}, we would find that we have $R(W) = R$.
\end{eg}

>>>>

Meanwhile, a different body of work has studied SYM $N=4$ theory from the point of view of Feynman integrals in twistor space \cite{Adamo:2011pv,Adamo:2012xe,  Boels:2007qn, Bullimore:2010pj}. These integrals are calculated via holomorphic Wilson loops. As with the Amplituhedron, each Wilson loop represents the sum of a family of $N^kMHV$ Feynman diagrams. Each of the Feynman integrands in this sum associates a volume form to a convex space, parallell to the Amplituhedron \cite{CachazoSvrcekWitten, Hodges2013}. However, the geometric objects decomposing the Wilson loops are different from the geometric object decomposing the Amplituhedron.

Wilson loop diagrams, as we will study them, are objects given by a perturbative expansion of the holomorphic Wilson loop in twistor space.
Classically, the interactions of the theory were studied as maximal helicity violating diagrams ($MHV$ diagrams), next-to-maximal helicity violating diagrams, and so on, ($N^kMHV$ diagrams) in momentum space. Adamo and Mason, in \cite{Adamo:2011pr}, gave an elegant formulation for the $N^kMHV$ diagrams in twistor space. The Wilson loop diagram perspective of this paper is dual to this twistor representation of $N^kMHV$ diagrams.
The objects are closely related and carry the same information.  We choose to emphasize the dual perspective by our focus on the Wilson loop diagrams.

@@

%%%%PARAGRAPH TO POTENTIALLY MOVE%%%%%%
As described above, each integrand associated to a Wilson loop diagram gives the volume of a convex polytope. However, each individual tree level integral has singularities. These singularities are of two types: physical and spurious.  The physical singularities come from special kinematical points and we will not consider them in this paper.  The spurious singularities come from zeros of the denominator of the integral, and hence are accessible to our combinatorial techniques.  SYM $N=4$ is a finite theory so we only expect to see the physical singularites in the overall amplitude.  Consequently, the spurious singularities are artifacts of how the integrals are represented and must cancel in the calculation of a tree level scattering amplitude, though the details of how the cancellations come about remain unclear. The cancellation has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$-dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto \cite{generalcombinatoricsI}.

@@

%%%%%POTENTIALLY MOVE PARAGRAPH HERE %%%%%
%As described above, each integrand associated to a Wilson loop diagram gives the volume of a convex polytope. However, each individual tree level integral has singularities. These singularities are of two types: physical and spurious.  The physical singularities come from special kinematical points and we will not consider them in this paper.  The spurious singularities come from zeros of the denominator of the integral, and hence are accessible to our combinatorial techniques.  SYM $N=4$ is a finite theory so we only expect to see the physical singularites in the overall amplitude.  Consequently, the spurious singularities are artifacts of how the integrals are represented and must cancel in the calculation of a tree level scattering amplitude, though the details of how the cancellations come about remain unclear. The cancellation has been conjectured in general \cite{Hodges2013} and verified explicitly in a few cases \cite{casestudy, HeslopStewart}, but it is hard to prove in general due to the fact that the relationship between Wilson loop diagrams and $3k$-dimensional positroid cells of $\Gr(k,n)$ is neither one-to-one nor onto \cite{generalcombinatoricsI}.

%To see the spurious poles explicitly, 
One may also interpret the functional $I(W)$ as associating a volume to each cell $\Sigma(W)$ \cite{wilsonloop, Amplituhedronsquared, HeslopStewart}, where the volume is determined by the external particles involved. Specifically, the integrand is written in terms of the elements of $C(W)$ as  \begin{equation} \label{eq:omega(W) def}\Omega(W) = \frac{\prod_{r=1}^{|\cP|} \prod_{v \in V(p_r)} \textrm{d}x_{p_r}}{R(W)} \;, \end{equation} multiplied by a $\delta$ function that evaluates the matrix $C(W)$ on the external particles. The denominator $R(W)$ is given in Definition~\ref{def R(W)} below.

@@

\begin{lem}\label{lem sian}
  Let $W$ be a weakly admissible Wilson loop diagram with at least 5 vertices and in which each vertex supports at least one propagator.  Then at least one of the following two conditions holds.
  \vspace{-0.5em}
  \begin{enumerate}
    \item The diagram $W$ has a propagator of length at most 6 with a propagator of length 2 on one side of it and nothing else on that side.\label{item big and 2}
    \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+2)$, the second is $(j, j+2)$, no other propagator has an end between vertices $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
  \end{enumerate}
See Figure~\ref{fig: small configs} for an illustration of the two configurations.
\end{lem}

@@

Since each propagator is removed by the algorithm after it contributes, each propagator contributes exactly once to $I_i$, making the above ordering well defined.
Note that different $I_*$ impose different orderings on the propagators. Furthermore, we will see below that this ordering respects the ordering of vertices in $I_i$, i.e. if $p_j$ occurs before $p_l$ in the ordering imposed by $I_i$, then we also have $I_i(p_j) <_i I_i(p_l)$. This will follow directly from Corollary \ref{GN alg well defined}.
\end{rmk}

@@

To construct $I_1$ we start at vertex 1, so we set $i=1$  and $I_1 = \emptyset$.
\begin{itemize}
\item Begin at $j = 1$. Since $\Prop(1) = \{q,r\}$ and $r$ is the clockwise-most of these propagators, $r$ contributes at this step. We let $I_1 = \{1\}$ and remove propagator $r$ from the diagram. 
\item Set $j = 2$. $\Prop(2) = \{p,q\}$, with $q$ being the clockwise-most of these propagators, so $q$ contributes at this step. We now have $I_1 = \{1,2\}$ and propagator $q$ is removed.
\item Set $j = 3$. $\Prop(3) = \{p\}$, so we have $I_1 = \{1,2,3\}$ and we remove propagator $p$. The only remaining propagator in the diagram is $s$.
\item Set $j = 4$. Since $p$ and $q$ were removed in earlier steps, we now have $\Prop(4) = \emptyset$.
\item Set $j = 5$. $\Prop(5) = \{s\}$, and we have $I_1 = \{1,2,3,5\}$.
\end{itemize}
There are no propagators left in the diagram, so the algorithm terminates and we have ${I_1 = \{1,2,3,5\}}$, which we write more compactly as $1235$. 
%So the propagators are ordered $r,q,p,s$ with respect to $I_1$, and 
$I_1$ viewed as a function is given by
\[I_1: \cP \longrightarrow [n] : \quad I_1(r) = 1,\quad I_1(q) = 2, \quad I_1(p) = 3, \quad I_1(s) = 5.\]
Applying the algorithm for all 8 starting vertices, we obtain the sets
\[1235, 2356, 3456, 4567, 5671, 6712, 7812, 8123.\]
The reader can easily verify that this sequence of $k$-sets satisfies the definition of a Grassmann necklace, and can (with significantly more work) also verify that this Grassmann necklace defines the positroid $M(W)$ associated to the Wilson loop diagram $W$ above. We will prove this in general shortly.
\end{eg}

@@

\begin{figure}
\[
\begin{tikzpicture}[baseline=(current bounding box.east)]
	\begin{scope}
	\drawWLDfragment[8]{4}{0.3}
	%\drawnumbers % use this to debug
	%\clip (\zero + 1.5*\step:1.5*\radius) rectangle (345:{\radius});
	\centerarc[linehighlight](0,0)(\zero + 2.8*\step:\zero + 6.2*\step:\radius)
	\newnode[below]{1}{i}
	\newnode[below]{2}{i+1}
	\newnode[below]{3}{l}
	\newnode[below]{4}{l+1}
	\newnode[below]{5}{l+2}
	\newnode[below]{6}{l+3}
	\newnode[below]{7}{j}
	\newnode[below]{8}{\quad j+1}
	%\node[rotate=-15] at (\zero + 2.7*\step:\radius) {\Large $($};
	%\node[rotate=15] at (\zero + 6.3*\step:\radius) {\Large $)$};
	\node at (\zero + 4.5*\step:\radius*0.85) {\em \scriptsize up to 4 vertices here};
	\begin{scope}
	\clipcenterarc(0,0)(\startpoint-10:\endpoint+10:\radius)
		\draw[smallpropagator] (\zero+1.3*\step:\radius*1.2) to [bend left = 40] (\zero + 7.7*\step:\radius*1.2); 
	\node at (\zero + 4.5*\step:\radius*0.5){\footnotesize $q$};
\end{scope}
\end{scope}
\end{tikzpicture}
\]
\caption{Diagram $V$ is $W$ with $p$ removed; there are no propagators inside $q = (i,j)$, though there may be up to 4 non-supporting vertices labelled $l, l+1, \ldots l+3$.}
\label{fig V diagram}
\end{figure}

@@

We first calculate $I^{W}_w$ for a starting vertex ${w \in [n]\backslash \{l, l+1, \ldots,j,j+1\}}$. Note that $p$ has no effect on other propagators for starting vertices in this range (since $p$ will be the final propagator encountered by the algorithm) so if $r \neq p$, then $I_w^W(r) = I_w^V(r)$. Meanwhile, the value of $I^{W}_w(p)$ depends on which step in the algorithm the propagator $q$ contributes a vertex in the diagram $V$, i.e. on the value of $I^{V}_w(q)$. Thus, if $w\in J_q^{V}(i)$ then 
    \[
    I_w^{W}(r) =  \begin{cases}
        \max\{i+1, m\} & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p\;,
      \end{cases} 
    \]
    while if $w\in J_q^{V}(i+1)$ or $w\in J_q^{V}(j)$ then
    \[
    I_w^{W}(r) =  \begin{cases}
        l & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p \;.
      \end{cases} 
      \]
We also need to understand $I^{W}_w$ for $w \in \{l,l+1,\ldots,j,j+1\}$. For the majority 
%$w \in [l, l+a-1]$} 
%I left this as a comment so we can add it in if necessary, but I don't think we need this level of precision in this sentence: we're just signposting what we're going to do in detail shortly.
of these vertices, we use the following observation: if $p$ is the first propagator to be assigned a value by $I_w^{W}$, then the remainder of $I_w^{W}$ proceeds identically to the assignments of $I^{V}_{w+1}$ (recall Remark~\ref{rmk algorithm locally same}).  Thus we have for any $0\leq b <a$
    \[
    I_{l+b}^{W}(r) = \begin{cases}
      l+b & \text{if } r=p\\
      I_{l+b+1}^{V}(r) & \text{if } r\neq p\;.
    \end{cases}
    \]
Similarly, if $j$ is in the support of $p$, then we have
     \[
       I_j^{W}(r) = \begin{cases}
         j & \text{if $r=p$ and $j$ is in the support of $p$}\\
         I_{j+1}^{V}(r) & \text{if $r\neq p$ and $j$ is in the support of $p$} \;.
       \end{cases} 
       \]
If $j$ is not in the support of $p$, then we must be in Case 2 of Figure~\ref{fig 3 cases} with two vertices in the right hand region.  In this case, if we start the algorithm at $j$ we need to know whether there will be any unassigned propagators other than $p$ when we reach vertex $i$, so as to know what $p$ contributes.

@@

For $w \in [n]\backslash\{j+1,m,m+1,m+2,m+3\}$, if $w\in J_q^{V}(i)$ or $w\in J_q^{V}(i+1)$ then
    \[
    I_w^{W}(r) =  \begin{cases}
        m & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p \;,
      \end{cases} 
    \]
    while if $w\in J_q^{V}(j)$ then
    \[
    I_w^{W}(r) =  \begin{cases}
        \max\{m, j+1\} & \text{if } r=p \\
        I_{w}^{V}(r) & \text{if } r\neq p
      \end{cases} \;.
    \]

@@

Let $W'$ be the diagram obtained from $W$ by removing the propagator $p$.  We have
\begin{align*}
  I_i^{W} \backslash \{i\} & = I_{i+1}^{W'} \\
  I_{i+1}^{W} \backslash \{i+1\} & = I_{i+2}^{W'}\;,
\end{align*}
since in both cases the algorithm in $W'$ proceeds identically to that in $W$ after assigning $p$. Since $m \neq i+1$, we have $m\in I_{i+1}^{W'}\setminus\{i+1\}$ but $m\not\in I_{i+2}^{W'}$, contradicting the minimality of $W$. This completes the proof.
\end{proof}

@@

Note that the positroid cells associated to the Amplituhedron are of dimension $4|\cP|$. In \cite[section 2]{non-orientable}, Agarwala and Marcott associated a Deodhar component\footnote{Since Deodhar components play no role in this paper, the interested reader is referred to \cite{non-orientable} for more details on this.} to each Wilson loop diagram, and showed that the dimension of this Deodhar component is the sum of $|\cP|$ and the dimension of the associated positroid cell.
%\[|\cP| + \text{ the dimension of associated positroid cell}.\]
Combining this with Theorem~\ref{thm dim}, we see that the Deodhar component associated to a Wilson loop diagram is $4|\cP|$-dimensional, showing that the geometry underlying the Wilson loop diagrams is consistent with the geometry underlying the Amplituhedron. It is worth noting that the Amplituhedon is defined by a projection of a set of $4|\cP|$ dimensional positroid cells (i.e. subspaces of $\Gr(k,n)$), while the corresponding $4|\cP|$-dimensional cells of the Wilson loop diagram lie in $\mathbb{G}_\R(k,n+1)$.
While it is conjectured that the geometry of the Amplituhedron is related to the geometry of the Wilson loop diagrams, in part due to their common physical origin, the $3 |\cP|$ dimensional positroid cells defined by the Wilson loop diagrams do not seem to bear any geometric relationship to the $4|\cP|$ dimensional positroid cells parametrized by the Amplituhedron.
%To  date, there is no evidence to suggest that the $3|\cP|$ dimensional positive cells of $\Gr(|\cP|, n)$ defining the Wilson loop diagrams are related to the $4|\cP|$ dimensional positive cells defining the Amplituhedron.  \sanote{This para adresses point 3 of report Y. Should there be a similar paragraph in the intro? Should it be moved?} \sanote{futzed some  more}

@@

\begin{lem}\label{lem I}
Let $W$ be an admissible Wilson loop diagram with $k\geq 1$ propagators, and suppose $W$ admits one of the configurations described in Lemma~\ref{lem good p}, with $p$ and $q$ (if $q$ exists) both of length 2. Let $V$ be $W$ with $p$ removed.  We can express $I_*^W$ in terms of $I_*^V$ as indicated below. If $k \in \{1, n-1, n-2, n\}$,

  \begin{align*}
    I_1^{W} & = I_1^{V} \cup \{n-3\} \\
    I_n^{W} & = I_1^{V} \cup \{n\} \\
    I_{n-1}^{W} & = I_n^{V} \cup \{n-1\} \\
    I_{n-2}^{W} & =
    \begin{cases}
      I_{n-2}^{V}\cup \{n-2\} & \text{if $n-2\not\in I_{n-2}^{V}$} \\
      I_{n-2}^{V}\cup \{n-1\} & \text{if $n-2\in I_{n-2}^{V}$, $n-1\not\in I_{n-2}^{V}$} \\
      (I_{n}^{V} \setminus \{n-5\})\cup \{n-1,n-2\} & \text{if $n-1, n-2\in I_{n-2}^{V}$}
    \end{cases} \;. \end{align*}
For all other $k$, i.e. $1<k<n-2$,
   \begin{align*}
    I_{k}^{W} & =
    \begin{cases}
      I_k^{V}\cup \{n-3\} & \qquad \qquad \qquad \qquad \text{if $n-3 \not\in I_k^{V}$}\\
      I_k^{V}\cup\{n-2\} & \qquad \qquad \qquad \qquad \text{if $n-3\in I_k^{V}$}
    \end{cases}
  \end{align*}
\end{lem}

@@

Finally, if $n-2$ and $ n-1$ are in $I_{n-2}^{V}$ then $I_{n-2}^W(q) = n-2$ and $I_{n-2}^W(p) = n-1$ as above, but some other propagator must have contributed $n-1$ to $I_{n-2}^{V}$ so we cannot use the same argument as above.  When, in the algorithm, the construction of $I_{n-2}^W$ reaches vertex $n$, only the propagators $p$ and $q$ have contributed; thus we proceed as in the construction of $I_n^{V}$ but without propagator $q$ by Remark \ref{rmk algorithm locally same}. By Lemma~\ref{vertex cyclic int lem} we know that $I_n^V(q) = n-5$, and from Remark \ref{clockwise ordering rem} we see that the only way this could occur is if $q$ was the last to contribute to $I_{n-2}^V$. %all other propagators in $V$ had already been assigned when we reached vertex $n-5$; thus $q$ was the final propagator contributing to $I_n^{V}$. 
Therefore, $I_{n-2}^{W} = (I_{n}^{V} \setminus \{n-5\}) \cup \{n-1, n-2\}$ in this case. This completes all cases for $I_{n-2}^{W}$.

@@

\begin{rmk}To avoid wordiness, we will refer to the row indexed by $i$ in the Le diagram as row $i$ or the $i$ row, and similarly for columns.  Note that the $i$ row in this sense is not the $i^{th}$ row since the indexing for Le diagrams does not label the rows sequentially starting at $1$, and so to avoid confusion we will not refer to the $i^{th}$ row. \end{rmk}

@@

\begin{eg}
Consider the Wilson loop diagram in Figure~\ref{fig R eg}. Assigning propagators $p$, $q$, $r$ to rows $1,2,3$ respectively, we obtain the matrix
\[
C(W) = \begin{bmatrix} a & b & 0 & 0 & 0 & c & d \\ e & f & 0 & 0 & g & h & 0 \\ i & j & 0 & k & l & 0 & 0 \end{bmatrix}.
\]
The Grassmann necklace of this diagram is
\begin{eqnarray*}\Big(I_1 = \{1,2,4\},\ I_2 = \{2,4,5\},\ I_3 = \{4,5,6\},\ I_4=\{4,5,6\},\\ I_5=\{5,6,7\},\ I_6 = \{6,7,1\},\ I_7=\{7,1,2\}\Big). \end{eqnarray*}  
Figure~\ref{fig R eg} indicates which vertex is contributed to $I_i$ by each propagator, for each $i \in [1,7]$.

@@

Finally, we have $r_1 = (af-be)k$.  Putting the previous calculations together, we obtain
\[
R = (af-be)kgbclhdi(ej-fi) \;,
\]
which is square-free and contains all factors of $\prod_{i=1}^{n}\Delta_{I_i}$. If one were to construct the denominator $R(W)$ associated to this Wilson loop diagram as per Definition~\ref{def R(W)}, we would find that we have $R(W) = R$.
\end{eg}
